\documentclass[9pt]{article}

\usepackage{fullpage}
\usepackage{longtable}
\usepackage{palatino}
\usepackage[usenames,svgnames]{xcolor}
\usepackage[pdftex,pdfusetitle,colorlinks=true,linkcolor=NavyBlue,citecolor=NavyBlue,urlcolor=NavyBlue,breaklinks=true,backref=page]{hyperref}

\newcommand{\smallfont}{\small}

\begin{document}

\begin{center}
{\huge \textbf{D\'avid P\'al}} \\[0.2cm]
\emph{Curriculum Vitae}
\end{center}

\vspace{0.2cm}

%
\noindent
%
\begin{minipage}{10cm}
\begin{tabular}{@{}ll}
E-mail:      & \href{mailto:davidko.pal@gmail.com}{\textbf{\texttt{davidko.pal@gmail.com}}} \\[0.1cm]
Web:         & \textbf{\url{http://david.palenica.com/}} \\[0.1cm]
Cell phone:  & +1 (646) 206 4832 \\[0.1cm]
% Home phone:  & +1 (917) 965 2187 \\[0.1cm]
\end{tabular}
\end{minipage}
%
\begin{minipage}{10cm}
800 High School Way, Apt. 242 \\
Mountain View, CA 94041 \\
USA \\
\end{minipage}


\vspace{0.3cm}

\noindent I am a machine learning researcher and a machine learning engineer.
My expertise is contextual bandits, ads ranking, ads auctions, discrete and
continuous optimization, big data, deep learning, spam filtering.

\section*{Employment}

\begin{longtable}{@{}lp{13cm}}
March 2024 -- present & \textbf{Sr. Staff Machine Learning Engineer at Coupang, Mountain View, CA} \\
& {\smallfont I am a part of search quality team. I work on machine learning models for search ranking.}
\\[0.3cm]
January 2021 -- February 2024 & \textbf{Staff Machine Learning Engineer at Instacart, New York, NY} \\
& {\smallfont I worked on
machine learning models for ads ranking. I built a system for training
click-through rate prediction models using Tensorflow. I worked on machine
learning models that allocate discount coupon to customers. I co-authored
three patents.}
\\[0.3cm]
May 2019 -- December 2020 & \textbf{Principal Applied Researcher at Expedia Group, New York, NY} \\
& {\smallfont I lead a team of 3 researchers building system for optimizing ad campaigns.
I built two libraries for solving large scale optimization problems using Apache Spark.}
\\[0.3cm]
Sep 2014 -- May 2019 & \textbf{Senior Research Scientist at Yahoo/Oath/Verizon Media Research, New York, NY} \\
& {\smallfont I designed and implemented machine learning models that filter
spam and phish emails by doing large scale clustering of emails using Hadoop
MapReduce and Apache Spark. I co-authored one patent. I published multiple
papers at NIPS and ICML. I served as a reviewer for COLT, ALT, ICML and area
chair for NIPS. I mentored 4 research interns.}
\\[0.3cm]
Sep 2011 -- Sep 2014 & \textbf{Software Engineer at Google, New York, NY} \\
& {\smallfont I was a backend engineer on the Google Ad Exchange team. I
designed, authored a patent for and implemented the ``passback'' ad auction
algorithm, which processes 100 billion ad impressions per day and generates
revenue of tens of billions of dollars per year. I also worked on the data
pipelines for reserve price optimization. The work was done in C++ and Python.}
\\[0.3cm]
Jul 2007 -- Sep 2007 & \textbf{Research Internship at Google, New York, NY} \\
& {\smallfont I designed an ad auction algorithm for AdWords that unifies GSP
(generalized second price) and VCG (Vickrey-Clarke-Groves) auctions and proved
mathematical theorems about it. The end result was an academic paper with description
of the algorithm and its properties that Google later used.}
\\[0.3cm]
Jun 2004 -- Dec 2004 & \textbf{Programmer at Applied Software Consultants, Bratislava, Slovakia} \\
& {\smallfont I was a software engineer in a small family-run company that
develops software for elementary schools and high schools. I worked on a desktop
application that keeps track of students, their grades, etc. The work was done in
C\# and PHP.}
\end{longtable}

\clearpage

\section*{Academics}

\begin{longtable}{@{}lp{13cm}}
January 2022 -- May 2022 & \textbf{Adjunct Professor at Tandon School of Engineering,} \\
& \textbf{New York University, New York, NY} \\
& {\smallfont I taight a graduate course "Statistical and Computational Foundations of Machine Learning".} \\
\\
Jul 2009 -- Jun 2011 & \textbf{Postdoctoral Fellow at Department of Computing Science,} \\
& \textbf{University of Alberta, Edmonton, AB, Canada} \\
& {\smallfont Advisor: Prof. Csaba Szepesv\'ari} \\
& {\smallfont I did research in machine learning and in statistics (contextual bandits, online optimization, entropy estimation).} \\
\\
Jan 2005 -- May 2009 & \textbf{Ph.D. in Computer Science, School of Computer Science,} \\
& \textbf{University of Waterloo, Waterloo, ON, Canada} \\
& {\smallfont Advisor: Prof. Shai Ben-David} \\
& {\smallfont Ph.D. Thesis: Contributions to Unsupervised and Semi-Supervised Learning} \\
\\
Sep 1999 -- May 2004 & \textbf{``Magister Degree'' in Computer Science,} \\
& \textbf{Faculty of Mathematics, Physics and Informatics,} \\
& \textbf{Comenius University, Bratislava, Slovakia} \\
& {\smallfont Advisor: Prof. Martin \v{S}koviera} \qquad {\smallfont Thesis: Steiner Colorings of Cubic Graphs} \\
\end{longtable}


\section*{Technical Skills}

\begin{itemize}
\item Python, Java, Scala, C++, Apache Spark, MapReduce, Tensorflow, LaTeX
\end{itemize}

\section*{Service}

\begin{itemize}
\item Area chair of NIPS 2018, 2019
\item Program Committee member of COLT 2017, COLT 2024
\item Reviewer for ICML 2016--2018; NIPS 2008--2014, 2016; COLT 2007, 2008, 2016, 2019--2023; AISTATS 2017--2018; STOC 2008; AAAI 2016; IJCAI 2016; ALT 2022, 2023.
\item Organizer of the Internet Problem Solving Contest, \url{http://ipsc.ksp.sk/}, 2000 -- 2004, 2007
\item Organizer of correspondence seminars in mathematics and computer science for Slovak high school students 1999 -- 2004.
\end{itemize}

\section*{Awards}

\begin{itemize}
\item co-author of a patent: ``Distributed algorithm for solving the generalized knapsack problem'' (Application no. 63/407,644)
\item co-author of a patent: ``Accounting for variable dimensions of content items when positioning content items in a user interface having slots for displaying content items`` (US 20230109298 A1)
\item co-author of a patent: ``Message classification'' (US 20180159808 A1)
\item co-author of a patent: ``Allocation of content inventory units'' (US 20160364766 A1)
\item co-author of a patent: ``Passback auction'' (US 20140316922 A1)
\item David R. Cheriton Scholarship, 2007 -- 2009
\item COLT 2006 Best Student Paper Award
\item 15th place in ACM ICPC 2000, Central European Region
\item 14th place in ACM ICPC 1999, Central European Region
\item Bronze Medal, Central European Olympiad in Informatics 1999
\item Winner of Internet Problem Solving Contest 1999, High School Division
\item Top 10 at Slovak National Olympiad in Informatics in 1997, 1998, 1999
\item Top 10 at Slovak National Olympiad in Physics in 1999
\end{itemize}

\section*{Personal}

\begin{itemize}
\item Dual citizenship: Slovak Republic \& U.S.
\end{itemize}

\section*{References}
%
\begin{minipage}[t]{9cm}
Edo Liberty \\
CEO of Pinecone \\
LinkedIn: \\
\url{https://www.linkedin.com/in/edo-liberty-4380164/}
\end{minipage}
%
\begin{minipage}[t]{9cm}
S. Muthu Muthukrishnan \\
Vice President at Amazon \\
LinkedIn: \\
\url{https://www.linkedin.com/in/muthu-muthukrishnan-4344819/}
\end{minipage}

\vspace{1cm}

\noindent
\begin{minipage}[t]{9cm}
Prof. Shai Ben-David \\
David R. Cheriton School of Computer Science \\
University of Waterloo, ON, Canada \\
email: \href{mailto:shai@cs.uwaterloo.ca}{\texttt{shai@cs.uwaterloo.ca}} \\
www: \url{http://www.cs.uwaterloo.ca/~shai/}
\end{minipage}
%
\begin{minipage}[t]{9cm}
Prof. Csaba Szepesv\'ari \\
Department of Computing Science \\
University of Alberta, Edmonton, AB, Canada \\
email: \href{mailto:szepesva@cs.ualberta.ca}{\texttt{szepesva@cs.ualberta.ca}} \\
www: \url{http://www.ualberta.ca/~szepesva/}
\end{minipage}


\renewcommand{\refname}{Publications}
\nocite{*}
\bibliography{publications}
\bibliographystyle{plainyr-rev}


\end{document}
